---
title: "CyTOF analysis with graph variables saving"
output: html_notebook
---

#IF running R/4.2
```{r}
.libPaths("/project/mcnamara-lab/myles_kim/R_library/4.2")
```



#clear all and load libraries
```{r, message=FALSE}
#rm(list = ls())
library(readxl, quietly = T)
library(tidyverse, quietly = T)
library(CATALYST, quietly = T)
library(FlowSOM, quietly = T)
library(flowCore, quietly = T)
library(igraph, quietly = T)
library(uwot, quietly = T)
library(ggpubr)
#library(tictoc) Never use this
#library(leiden) #this asks a question. Can I provide 'yes' as default?
```


#Read panel info
```{r}
#panel_read <- read_csv("/project/mcnamara-lab/myles_kim/RedHart2_v_CAVA/panelfile_RH2vCAVA_tcelll.csv")
#save(panel_read, file = "paneldata.RData")
panel_read <- read_csv("../panelfile_nometal_draft1.csv")

#panel_read[31,3]="type" #CD27 as type

table(panel_read$marker_class)


```



#Read or make metadata
```{r}

#load("./metadata.RData")

data_folder <- "/project/mcnamara-lab/FCS_folder/REDHART2_v_CAVA/New Subpopulation Export JC/Tcells_colfixed/"

files_fcs <- list.files(data_folder, pattern = "fcs$")

metadata = data.frame(file_name = files_fcs)
metadata$sample_id = gsub("Colfixed_", "", files_fcs)
metadata$sample_id = gsub(".fcs", "", metadata$sample_id)

patient_id1 = stringr::str_match(files_fcs, "[1-9][0-9][0-9][0-9]")[,1] 
patient_id1[which(is.na(patient_id1))] = 
  stringr::str_match(files_fcs[which(is.na(patient_id1))], "[1-9][0-9][0-9]")[,1] 
patient_id1[which(is.na(patient_id1))] =
  stringr::str_match(files_fcs[which(is.na(patient_id1))], "HBO19")[,1]

metadata$patient_id = patient_id1

rm(patient_id1)

metadata$condition = "VEH"
metadata$condition[  which(!is.na(stringr::str_match(files_fcs, "US")[,1]))  ] <- "VEH"
metadata$condition[  which(!is.na(stringr::str_match(files_fcs, "VEH")[,1]))  ] <- "VEH"
metadata$condition[  which(!is.na(stringr::str_match(files_fcs, "IL-1b")[,1]))  ] <- "IL1b"
metadata$condition[  which(!is.na(stringr::str_match(files_fcs, "IL-6")[,1]))  ] <- "IL6"


save(metadata, file = "metadata.RData")
```



#Read FCS's into sce
```{r}

sce <- prepData(data_folder, panel = panel_read, md = metadata, features = panel_read$fcs_colname)
Sys.time()

```

```{r}


m = "CD8"
count_data = sce@assays@data$counts[m,]


df_count_data_q100 <- as.data.frame(count_data)

ggplot(  df_count_data_q100, aes(x= asinh(count_data/0.1)   )   ) + 
    geom_histogram(aes(y=..density..),bins=87, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "New"))

ggplot(  df_count_data_q100, aes(x= asinh(count_data/0.01)   )   ) + 
    geom_histogram(aes(y=..density..),bins=87, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "New"))

ggplot(  df_count_data_q100, aes(x= asinh(count_data/0.001)   )   ) + 
    geom_histogram(aes(y=..density..),bins=87, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "New"))

ggplot(  df_count_data_q100, aes(x= log((count_data+1)/0.01)   )   ) + 
    geom_histogram(aes(y=..density..),bins=87, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "New"))

```



```{r}

#cofactors <- readRDS("../Various_cofactors_for_asinh.rds")
all_markers <- c(type_markers(sce), state_markers(sce))




q95_all_markers <- lapply(all_markers, function(m){
  
  q95 <- quantile(sce@assays@data$counts[m,], probs = 0.95)
  
})

q95_point <- data.frame(marker = all_markers, q95 = unlist(q95_all_markers))


q95_point$cofactor <- 1
for (ii in 1:length(q95_point$cofactor)){
  
  q95_point$cofactor[ii] <- sort(c(1, 5, q95_point$q95[ii]/10))[2]  
  
}

save(q95_point, file = "q95_cofactor.Rdata")
```




#Two transformation comparison
```{r}

#ii = 0
#p_list <- list()
# all_markers = c(type_markers(sce), state_markers(sce))
# #m=all_markers[1]
# 
# p_list <- lapply(all_markers, function(m){
#   
#   
#   count_data = sce@assays@data$counts[m,]
#   q95 <- quantile(count_data, probs = c(0.95))
#   
#   df_count_data_q100 <- as.data.frame(count_data)
#   
# 
#   p_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
#     geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
#   
#   
# })
#   
#   
# 
# q_list <- lapply(all_markers, function(m){
#   
#   
#   count_data = sce@assays@data$counts[m,]
#   q95 <- quantile(count_data, probs = c(0.95))
#   
#   df_count_data_q100 <- as.data.frame(count_data)
#   
# 
#   q_list_temp <- ggplot(  df_count_data_q100, aes(x=log10(count_data/(q95/10)+1) )   ) + 
#     geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: log10( /(q95/10) + 1)"))
#   
#   
# })
# 
# fig_list = list()
# 
# for (ii in 1:length(q_list)){
#   
#   
#      fig_list[[2*ii-1]] = p_list[[ii]]
#      fig_list[[2*ii]] = q_list[[ii]]
# }
# 
# # 
# p <- ggarrange(plotlist = fig_list, common.legend = T, ncol = 2, nrow = 12)  #, ncol = 6
# 
# pdf(paste0("two_transformation_comparison.pdf"), height = 24, width = 12)
# p
# dev.off()
# 
# p_list[[1]]
# 
# ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
#     geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  


```




#Two transformation comparison #-1/3
```{r}


a = 2.1609
#ii = 0
#p_list <- list()
all_markers = c(type_markers(sce), state_markers(sce))
#m=all_markers[1]

p_list <- lapply(all_markers, function(m){
  
  
  count_data = sce@assays@data$counts[m,]
  q95 <- quantile(count_data, probs = c(0.95))
  
  df_count_data_q100 <- as.data.frame(count_data)
  

  # p_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
  #   geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  
    p_list_temp <- ggplot(  df_count_data_q100, aes(x=(2/a)*asinh( sqrt(a*count_data)  ) )   ) + 
    geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "New"))
  
  
})
  
  

q_list <- lapply(all_markers, function(m){
  
  
  count_data = sce@assays@data$counts[m,]
  q95 <- quantile(count_data, probs = c(0.95))
  
  df_count_data_q100 <- as.data.frame(count_data)
  

  # q_list_temp <- ggplot(  df_count_data_q100, aes(x=log10(count_data/(q95/10)+1) )   ) + 
  #   geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: log10( /(q95/10) + 1)"))
  
  
  q_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
    geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))

  
})

fig_list = list()

for (ii in 1:length(q_list)){
  
  
     fig_list[[2*ii-1]] = p_list[[ii]]
     fig_list[[2*ii]] = q_list[[ii]]
}

# 
p <- ggarrange(plotlist = fig_list, common.legend = T, ncol = 2, nrow = 12)  #, ncol = 6

pdf(paste0("two_transformation_comparison_sqrt2_v_q95over10_1.pdf"), height = 24, width = 12)
p
dev.off()
# 
# p_list[[1]]
# 
# ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
#     geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  


```


#Two transformation comparison #0/3
```{r}

#ii = 0
#p_list <- list()
all_markers = c(type_markers(sce), state_markers(sce))
#m=all_markers[1]

p_list <- lapply(all_markers, function(m){
  
  
  count_data = sce@assays@data$counts[m,]
  q95 <- quantile(count_data, probs = c(0.95))
  
  df_count_data_q100 <- as.data.frame(count_data)
  

  # p_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
  #   geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  
    p_list_temp <- ggplot(  df_count_data_q100, aes(x=(2/0.95)*asinh( sqrt(0.95*count_data)  ) )   ) + 
    geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "New"))
  
  
})
  
  

q_list <- lapply(all_markers, function(m){
  
  
  count_data = sce@assays@data$counts[m,]
  q95 <- quantile(count_data, probs = c(0.95))
  
  df_count_data_q100 <- as.data.frame(count_data)
  

  # q_list_temp <- ggplot(  df_count_data_q100, aes(x=log10(count_data/(q95/10)+1) )   ) + 
  #   geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: log10( /(q95/10) + 1)"))
  
  
  q_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
    geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))

  
})

fig_list = list()

for (ii in 1:length(q_list)){
  
  
     fig_list[[2*ii-1]] = p_list[[ii]]
     fig_list[[2*ii]] = q_list[[ii]]
}

# 
p <- ggarrange(plotlist = fig_list, common.legend = T, ncol = 2, nrow = 12)  #, ncol = 6

pdf(paste0("two_transformation_comparison_sqrt_v_q95over10.pdf"), height = 24, width = 12)
p
dev.off()
# 
# p_list[[1]]
# 
# ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
#     geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  


```



#Two transformation comparison #1/3
```{r}

#ii = 0
#p_list <- list()
all_markers = c(type_markers(sce), state_markers(sce))
#m=all_markers[1]

p_list <- lapply(all_markers, function(m){
  
  
  count_data = sce@assays@data$counts[m,]
  q95 <- quantile(count_data, probs = c(0.95))
  
  df_count_data_q100 <- as.data.frame(count_data)
  

  # p_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
  #   geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  
    p_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(5)  ) )   ) + 
    geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /5)"))
  
  
})
  
  

q_list <- lapply(all_markers, function(m){
  
  
  count_data = sce@assays@data$counts[m,]
  q95 <- quantile(count_data, probs = c(0.95))
  
  df_count_data_q100 <- as.data.frame(count_data)
  

  # q_list_temp <- ggplot(  df_count_data_q100, aes(x=log10(count_data/(q95/10)+1) )   ) + 
  #   geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: log10( /(q95/10) + 1)"))
  
  
  q_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
    geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))

  
})

fig_list = list()

for (ii in 1:length(q_list)){
  
  
     fig_list[[2*ii-1]] = p_list[[ii]]
     fig_list[[2*ii]] = q_list[[ii]]
}

# 
p <- ggarrange(plotlist = fig_list, common.legend = T, ncol = 2, nrow = 12)  #, ncol = 6

pdf(paste0("two_transformation_comparison_5_v_q95over10.pdf"), height = 24, width = 12)
p
dev.off()
# 
# p_list[[1]]
# 
# ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
#     geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  


```



#Two transformation comparison #2/3
```{r}

#ii = 0
#p_list <- list()
all_markers = c(type_markers(sce), state_markers(sce))
#m=all_markers[1]

p_list <- lapply(all_markers, function(m){
  
  
  count_data = sce@assays@data$counts[m,]
  q95 <- quantile(count_data, probs = c(0.95))
  
  df_count_data_q100 <- as.data.frame(count_data)
  

  # p_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
  #   geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  
    p_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
    geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /q95/10)"))
  
  
})
  
  

q_list <- lapply(all_markers, function(m){
  
  
  count_data = sce@assays@data$counts[m,]
  q95 <- quantile(count_data, probs = c(0.95))
  
  df_count_data_q100 <- as.data.frame(count_data)
  

  # q_list_temp <- ggplot(  df_count_data_q100, aes(x=log10(count_data/(q95/10)+1) )   ) + 
  #   geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: log10( /(q95/10) + 1)"))
  
  
  cofactor = sort(c(1,5, q95/10))[2]
  #print(c(cofractor, q95/10))
  
  q_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(cofactor)  ) )   ) + 
    geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /[1~5])"))

  
})

fig_list = list()

for (ii in 1:length(q_list)){
  
  
     fig_list[[2*ii-1]] = p_list[[ii]]
     fig_list[[2*ii]] = q_list[[ii]]
}

# 
p <- ggarrange(plotlist = fig_list, common.legend = T, ncol = 2, nrow = 12)  #, ncol = 6

pdf(paste0("two_transformation_comparison_q95over10_v_q95over10_1to5.pdf"), height = 24, width = 12)
p
dev.off()
# 
# p_list[[1]]
# 
# ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
#     geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  


```





#Two transformation comparison #3/3
```{r}

#ii = 0
#p_list <- list()
all_markers = c(type_markers(sce), state_markers(sce))
#m=all_markers[1]

p_list <- lapply(all_markers, function(m){
  
  
  count_data = sce@assays@data$counts[m,]
  q95 <- quantile(count_data, probs = c(0.95))
  
  df_count_data_q100 <- as.data.frame(count_data)

  df_count_data_q95 <- as.data.frame(count_data[count_data<q95])
  colnames(df_count_data_q95)[1]="count_data"
  # p_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
  #   geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  
    p_list_temp <- ggplot(  df_count_data_q95, aes(x=count_data)   ) + 
    geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "95% range: raw"))
  
  
})
  
  

q_list <- lapply(all_markers, function(m){
  
  
  count_data = sce@assays@data$counts[m,]
  q95 <- quantile(count_data, probs = c(0.95))
  
  df_count_data_q100 <- as.data.frame(count_data)
  

  # q_list_temp <- ggplot(  df_count_data_q100, aes(x=log10(count_data/(q95/10)+1) )   ) + 
  #   geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: log10( /(q95/10) + 1)"))
  
  
  q_list_temp <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
    geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))

  
})

fig_list = list()

for (ii in 1:length(q_list)){
  
  
     fig_list[[2*ii-1]] = p_list[[ii]]
     fig_list[[2*ii]] = q_list[[ii]]
}

# 
p <- ggarrange(plotlist = fig_list, common.legend = T, ncol = 2, nrow = 12)  #, ncol = 6

pdf(paste0("two_transformation_comparison_raw_v_q95over10.pdf"), height = 24, width = 12)
p
dev.off()
# 
# p_list[[1]]
# 
# ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
#     geom_histogram(aes(y=..density..),bins=51, colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
  



```




```{r}

markers <- c(type_markers(sce), state_markers(sce))

q9599 <- data.frame(marker = markers)
rownames(q9599) = q9599$marker


q9599$q95 <- 1
q9599$q99 <- 1


for (m in markers){
  
  
   q9599[m, 2:3] = quantile(sce@assays@data$counts[m, ], probs = c(0.95, 0.99))
  
  
}


saveRDS(q9599, "q9599.rds")

```




#Histogram for a few markers
```{r}
library(ggpubr)
m="p-NF-kB"
count_data = sce@assays@data$counts[m,]

length(which(count_data == 0))/length(count_data)

quantile(count_data, probs = c(0.5, 0.6, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))


q95 <- quantile(count_data, probs = c(0.95))
q975 <- quantile(count_data, probs = c(0.975))

count_data_q95 <- count_data[count_data<q95]

#hist(count_data_q95)                     # Store histogram info
# my_hist$counts <- cumsum(my_hist$counts)    # Change histogram counts
# plot(my_hist)



df_count_data_q100 <- as.data.frame(count_data)
# ggplot(  df_count_data_q100, aes(x=count_data)   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range"))
# 

df_count_data_q95 <- as.data.frame(count_data_q95)

# ggplot(  df_count_data_q95, aes(x=count_data_q95)   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "upto 95%"))
# 
# 
# ggplot(  df_count_data_q100, aes(x=asinh(count_data/5) )   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /5)"))
# 
# ggplot(  df_count_data_q95, aes(x=asinh(count_data_q95/5) )   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "upto 95%: asinh( /5)"))
# 
# ggplot(  df_count_data_q95, aes(x=asinh(count_data_q95/(q95/10)) )   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "upto 95%: asinh( /0.1q95)"))

p_list <- list()

p_list[[1]] <- ggplot(  df_count_data_q95, aes(x=count_data_q95)   ) +
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "upto 95%"))
p_list[[1]]


p_list[[2]] <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/5) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /5)"))
p_list[[2]]


p_list[[3]] <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/cofactors[m, "q95_2p998"]) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
p_list[[3]]


p_list[[4]] <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/cofactors[m, "flowVS"]) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /flowVS)"))
p_list[[4]]

p_list[[5]] <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/cofactors[m, "q95_5"]) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@5)"))
p_list[[5]]


p_list[[6]] <- ggplot(  df_count_data_q100, aes(x=log10(count_data/0.1+1) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: log10( /0.1 + 1)"))
p_list[[6]]



p2 <- ggarrange(plotlist = p_list, common.legend = T, ncol = 3, nrow = 2)  #, ncol = 6

pdf(paste0("six_histo_",m,".pdf"), height = 4, width = 11)
p2
dev.off()

```



#Histogram for a few markers
```{r}
library(ggpubr)
m="CD8"
count_data = sce@assays@data$counts[m,]

length(which(count_data == 0))/length(count_data)

quantile(count_data, probs = c(0.5, 0.6, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))


q95 <- quantile(count_data, probs = c(0.95))
q975 <- quantile(count_data, probs = c(0.975))

count_data_q95 <- count_data[count_data<q95]

#hist(count_data_q95)                     # Store histogram info
# my_hist$counts <- cumsum(my_hist$counts)    # Change histogram counts
# plot(my_hist)



df_count_data_q100 <- as.data.frame(count_data)
# ggplot(  df_count_data_q100, aes(x=count_data)   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range"))
# 

df_count_data_q95 <- as.data.frame(count_data_q95)


ggplot(  df_count_data_q100, aes(x=asinh(count_data/(q95/10)  ) )   ) + 
     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))


ggplot(  df_count_data_q100, aes(x=log10(count_data/(q95/10)+1) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: log10( /(q95/10) + 1)"))

##############

# 
# p_list <- list()
# 
# p_list[[1]] <- ggplot(  df_count_data_q95, aes(x=count_data_q95)   ) +
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "upto 95%"))
# p_list[[1]]
# 
# 
# p_list[[2]] <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/5) )   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /5)"))
# p_list[[2]]
# 
# 
# p_list[[3]] <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/cofactors[m, "q95_2p998"]) )   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@2.99)"))
# p_list[[3]]
# 
# 
# p_list[[4]] <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/cofactors[m, "flowVS"]) )   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /flowVS)"))
# p_list[[4]]
# 
# p_list[[5]] <- ggplot(  df_count_data_q100, aes(x=asinh(count_data/cofactors[m, "q95_5"]) )   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: asinh( /Q95@5)"))
# p_list[[5]]
# 
# 
# p_list[[6]] <- ggplot(  df_count_data_q100, aes(x=log10(count_data/0.1+1) )   ) + 
#     geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=paste(m, "full range: log10( /0.1 + 1)"))
# p_list[[6]]
# 
# 
# 
# p2 <- ggarrange(plotlist = p_list, common.legend = T, ncol = 3, nrow = 2)  #, ncol = 6
# 
# pdf(paste0("six_histo_",m,".pdf"), height = 4, width = 11)
# p2
# dev.off()

```






```{r}

m="CD45RO"
count_data = sce@assays@data$counts[m,]
quantile(count_data, probs = c(0.25, 0.5, 0.6, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))
q95 <- quantile(count_data, probs = c(0.95))

count_data_q95 <- count_data[count_data<q95]

hist(count_data_q95)                     # Store histogram info
# my_hist$counts <- cumsum(my_hist$counts)    # Change histogram counts
# plot(my_hist)

df_count_data_q95 <- as.data.frame(count_data_q95)

ggplot(  df_count_data_q95, aes(x=count_data_q95)   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=m)

ggplot(  df_count_data_q95, aes(x=asinh(count_data_q95/5) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=m)


ggplot(  df_count_data_q95, aes(x=asinh(count_data_q95/(q95/10)) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=m)

```

```{r}

m="CD56"
count_data = sce@assays@data$counts[m,]
quantile(count_data, probs = c(0.25, 0.5, 0.6, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))
q95 <- quantile(count_data, probs = c(0.95))

count_data_q95 <- count_data[count_data<q95]

hist(count_data_q95)                     # Store histogram info
# my_hist$counts <- cumsum(my_hist$counts)    # Change histogram counts
# plot(my_hist)

df_count_data_q95 <- as.data.frame(count_data_q95)

ggplot(  df_count_data_q95, aes(x=count_data_q95)   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=m)

ggplot(  df_count_data_q95, aes(x=asinh(count_data_q95/5) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=m)


ggplot(  df_count_data_q95, aes(x=asinh(count_data_q95/(q95/10)) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=m)
```



```{r}

m="CD8"
count_data = sce@assays@data$counts[m,]
quantile(count_data, probs = c(0.25, 0.5, 0.6, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))
q95 <- quantile(count_data, probs = c(0.95))

count_data_q95 <- count_data[count_data<q95]

hist(count_data_q95)                     # Store histogram info
# my_hist$counts <- cumsum(my_hist$counts)    # Change histogram counts
# plot(my_hist)

df_count_data_q95 <- as.data.frame(count_data_q95)

ggplot(  df_count_data_q95, aes(x=count_data_q95)   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() 


ggplot(  df_count_data_q95, aes(x=asinh(count_data_q95/5) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=m)


ggplot(  df_count_data_q95, aes(x=asinh(count_data_q95/(q95/10)) )   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title=m)



quantile(asinh(df_count_data_q95$count_data_q95/(q95/10)), probs = c(0.25, 0.5, 0.6, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))
```





```{r}

marker_list <- c(type_markers(sce), state_markers(sce))

cf=0.1

p_list <- lapply(marker_list, function(m){
  
  count_data = sce@assays@data$counts[m,]
  
  log10p1_count_data <- as.data.frame(log10(count_data/cf+1))
  
  colnames(log10p1_count_data) = "log10p1"
  
  p <- ggplot(  log10p1_count_data, aes(x=log10p1)   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title = m)
  
})





p_list_t <- list()
k=0
for (ii in (1+k):(6+k)){
p_list_t[[ii-k]] <- p_list[[ii]]  
}

p2 <- ggarrange(plotlist = p_list_t, common.legend = FALSE, ncol = 2, nrow = 3)  #, ncol = 6
pdf("A000_histo_log10p1_I.pdf", height = 8, width = 6)
p2
dev.off()


p_list_t <- list()
k=6
for (ii in (1+k):(6+k)){
p_list_t[[ii-k]] <- p_list[[ii]]  
}

p2 <- ggarrange(plotlist = p_list_t, common.legend = FALSE, ncol = 2, nrow = 3)  #, ncol = 6
pdf("A000_histo_log10p1_II.pdf", height = 8, width = 6)
p2
dev.off()

p_list_t <- list()
k=12
for (ii in (1+k):(6+k)){
p_list_t[[ii-k]] <- p_list[[ii]]  
}

p2 <- ggarrange(plotlist = p_list_t, common.legend = FALSE, ncol = 2, nrow = 3)  #, ncol = 6
pdf("A000_histo_log10p1_III.pdf", height = 8, width = 6)
p2
dev.off()


p_list_t <- list()
k=18
for (ii in (1+k):(6+k)){
p_list_t[[ii-k]] <- p_list[[ii]]  
}

p2 <- ggarrange(plotlist = p_list_t, common.legend = FALSE, ncol = 2, nrow = 3)  #, ncol = 6
pdf("A000_histo_log10p1_IV.pdf", height = 8, width = 6)
p2
dev.off()




m = "CD45RO"

count_data = sce@assays@data$counts[m,]

log10p1_count_data <- as.data.frame(log10(count_data/0.01+1))

colnames(log10p1_count_data) = "log10p1"

ggplot(  log10p1_count_data, aes(x=log10p1)   ) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title = m)

# h <- hist(log10p1_count_data , freq=FALSE, breaks = 30)
# h <- as.data.frame(h$density)
# p<-ggplot(log10p1_count_data, aes(x=log10p1)) + 
#   geom_histogram(color="black", fill="white")
# p


ggplot(  log10p1_count_data, aes(x=log10p1)   ) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title = m)

#+ geom_density(alpha=.2, fill="#FF6666") 

# 
# range(count_data)
# quantile(count_data, probs = c(0.5,0.6,0.65, 0.675,0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))
# hist(count_data, freq=FALSE)
# hist(count_data, freq=FALSE, breaks=20)
# 
# count_data_high <- count_data[count_data >0.99]
# hist(count_data_high, freq=FALSE)
# 
# h <- hist(count_data, breaks=c(0, 0.1, 1, 5, 10, 50, 100, 1000, max(count_data)))
# 
# 
# hist(log_count_data, freq=FALSE, breaks = 30)
# 
# 
# 
# my_hist <- hist(log_count_data)                     # Store histogram info
# my_hist$counts <- cumsum(my_hist$counts)    # Change histogram counts
# plot(my_hist) 


```


```{r}



marker_list <- c(type_markers(sce), state_markers(sce))

p_list <- lapply(marker_list, function(m){
  
  exprs_data = sce@assays@data$exprs[m,]
  
  exprs_data <- as.data.frame( exprs_data )
  
  colnames(exprs_data) = "tfed_by_cofactor5"
  
  p <- ggplot(  exprs_data, aes(x=tfed_by_cofactor5)   ) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white") + theme_bw() + labs(title = m)
  
})





p_list_t <- list()
k=0
for (ii in (1+k):(6+k)){
p_list_t[[ii-k]] <- p_list[[ii]]  
}

p2 <- ggarrange(plotlist = p_list_t, common.legend = FALSE, ncol = 2, nrow = 3)  #, ncol = 6
pdf("A000_histo_cofactor5_I.pdf", height = 8, width = 6)
p2
dev.off()


p_list_t <- list()
k=6
for (ii in (1+k):(6+k)){
p_list_t[[ii-k]] <- p_list[[ii]]  
}

p2 <- ggarrange(plotlist = p_list_t, common.legend = FALSE, ncol = 2, nrow = 3)  #, ncol = 6
pdf("A000_histo_cofactor5_II.pdf", height = 8, width = 6)
p2
dev.off()

p_list_t <- list()
k=12
for (ii in (1+k):(6+k)){
p_list_t[[ii-k]] <- p_list[[ii]]  
}

p2 <- ggarrange(plotlist = p_list_t, common.legend = FALSE, ncol = 2, nrow = 3)  #, ncol = 6
pdf("A000_histo_cofactor5_III.pdf", height = 8, width = 6)
p2
dev.off()


p_list_t <- list()
k=18
for (ii in (1+k):(6+k)){
p_list_t[[ii-k]] <- p_list[[ii]]  
}

p2 <- ggarrange(plotlist = p_list_t, common.legend = FALSE, ncol = 2, nrow = 3)  #, ncol = 6
pdf("A000_histo_cofactor5_IV.pdf", height = 8, width = 6)
p2
dev.off()
```





```{r}

m="CD8"
count_data = sce@assays@data$counts[m,]

log_count_data <- log10(count_data+1)

range(count_data)
quantile(count_data, probs = c(0.5,0.6,0.65, 0.675,0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))
hist(count_data, freq=FALSE)
hist(count_data, freq=FALSE, breaks=20)


count_data_high <- count_data[count_data >0.99]
hist(count_data_high, freq=FALSE)


h <- hist(count_data, breaks=c(0, 0.1, 1, 5, 10, 50, 100, 2003))


h <- hist(log_count_data, freq=FALSE)



my_hist <- hist(log_count_data)                     # Store histogram info
my_hist$counts <- cumsum(my_hist$counts)    # Change histogram counts
plot(my_hist) 


```


```{r}

m="CD4"
count_data = sce@assays@data$counts[m,]

log_count_data <- log10(count_data+1)

range(count_data)
quantile(count_data, probs = c(0.5,0.6,0.65, 0.675,0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))
hist(count_data, freq=FALSE)
hist(count_data, freq=FALSE, breaks=20)

count_data_high <- count_data[count_data >0.99]
hist(count_data_high, freq=FALSE)

h <- hist(count_data, breaks=c(0, 0.1, 1, 5, 10, 50, 100, 1000, max(count_data)))


h <- hist(log_count_data, freq=FALSE)

 hist(log_count_data, freq=FALSE, breaks = 30)  

my_hist <- hist(log_count_data)                     # Store histogram info
my_hist$counts <- cumsum(my_hist$counts)    # Change histogram counts
plot(my_hist) 


```



```{r}

m="CD45RO"
count_data = sce@assays@data$counts[m,]

log_count_data <- log10(count_data+1)

range(count_data)
quantile(count_data, probs = c(0.5,0.6,0.65, 0.675,0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))
hist(count_data, freq=FALSE)
hist(count_data, freq=FALSE, breaks=20)

count_data_high <- count_data[count_data >0.99]
hist(count_data_high, freq=FALSE)

h <- hist(count_data, breaks=c(0, 0.1, 1, 5, 10, 50, 100, 1000, max(count_data)))


h <- hist(log_count_data, freq=FALSE)



my_hist <- hist(log_count_data)                     # Store histogram info
my_hist$counts <- cumsum(my_hist$counts)    # Change histogram counts
plot(my_hist) 


```

```{r}

m="CD197"
count_data = sce@assays@data$counts[m,]

log_count_data <- log10(count_data+1)

range(count_data)
quantile(count_data, probs = c(0.5,0.6,0.65, 0.675,0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.975, 0.99))
hist(count_data, freq=FALSE)
hist(count_data, freq=FALSE, breaks=20)

count_data_high <- count_data[count_data >0.99]
hist(count_data_high, freq=FALSE)

h <- hist(count_data, breaks=c(0, 0.1, 1, 5, 10, 50, 100, 1000, max(count_data)))


h <- hist(log_count_data, freq=FALSE)

hist(log_count_data, breaks = 40, freq=FALSE)

my_hist <- hist(log_count_data)                     # Store histogram info
my_hist$counts <- cumsum(my_hist$counts)    # Change histogram counts
plot(my_hist) 


```

# if data is already asinh transformed
```{r}

sce@assays@data$exprs <- sce@assays@data$counts
Sys.time()
```


# sample-wise marker expression profiles
```{r}


p <- list()
marker_index <- which(is.na(stringr::str_match(substr(rownames(sce@assays@data$counts),1,2), "[0-9][0-9]")[,1]))
markers <- rownames(sce@assays@data$counts)[marker_index]

type_marker_list <- markers[which(markers %in% type_markers(sce))]
state_marker_list <- markers[which(markers %in% state_markers(sce))]
none_marker_list <- setdiff(markers, type_marker_list)
none_marker_list <- setdiff(none_marker_list, state_marker_list)

ii=0

for (m in type_marker_list){
  
  data_4_plot <- data.frame(expression = sce@assays@data$exprs[m,], sample_id = sce$sample_id)
  
  ii <- ii +1
  p[[ii]] <-    ggplot(data_4_plot, aes(expression, color = sample_id))+geom_density(show.legend = FALSE) +
    theme_bw() + labs(title = paste("type marker:", m) ) + 
    xlab(NULL)+ylab(NULL) + 
    theme(aspect.ratio=2/4)+ theme(axis.text.x = element_text(size = 10)) + 
    theme(axis.text.y = element_text(size = 11, color = "black")) +
    theme(axis.text.x = element_text(size = 11, color = "black")) +
    theme(axis.line = element_line(lineend = "square"))

}

for (m in state_marker_list){
  
  data_4_plot <- data.frame(expression = sce@assays@data$exprs[m,], sample_id = sce$sample_id)
  
  ii <- ii +1
  p[[ii]] <-    ggplot(data_4_plot, aes(expression, color = sample_id))+geom_density(show.legend = FALSE) +
    theme_bw() + labs(title = paste("state marker:", m) ) + 
    xlab(NULL)+ylab(NULL) + 
    theme(aspect.ratio=2/4)+ theme(axis.text.x = element_text(size = 10)) + 
    theme(axis.text.y = element_text(size = 11, color = "black")) +
    theme(axis.text.x = element_text(size = 11, color = "black")) +
    theme(axis.line = element_line(lineend = "square"))

}


for (m in none_marker_list){
  
  data_4_plot <- data.frame(expression = sce@assays@data$exprs[m,], sample_id = sce$sample_id)
  
  ii <- ii +1
  p[[ii]] <-    ggplot(data_4_plot, aes(expression, color = sample_id))+geom_density(show.legend = FALSE) +
    theme_bw() + labs(title = paste("none marker:", m) ) + 
    xlab(NULL)+ylab(NULL) + 
    theme(aspect.ratio=2/4)+ theme(axis.text.x = element_text(size = 10)) + 
    theme(axis.text.y = element_text(size = 11, color = "black")) +
    theme(axis.text.x = element_text(size = 11, color = "black")) +
    theme(axis.line = element_line(lineend = "square"))

}

p2 <- ggarrange(plotlist = p, common.legend = FALSE, ncol = 5, nrow = 3)  #, ncol = 6
pdf("F000_all_marker_expression_profile.pdf", height = 7, width = 12)
p2
dev.off()


```



